Conservation of interaction partners between related plants varies widely across communities and between plant families - Supporting Information

### 2019-06-25 manuscript/supporting_info.tex
supporting info ready

    Only five families were sufficiently well-represented to fit models for shared herbivores: \emph{Asteraceae}, \emph{Fabaceae}, \emph{Melastomataceae}, \emph{Poaceae}, and \emph{Rubiaceae}. All were also well-represented enough to fit models for shared pollinators.

    In total, there were 48 families which were well-represented enough to fit models for shared pollinators. For 13 of these, we obtained singular fits.
    Singular fits were obtained for \emph{Amaranthaceae}, \emph{Araliaceae}, \emph{Boraginaceae},
    \emph{Campanulaceae}, \emph{Caryophyllaceae}, \emph{Ericaceae}, \emph{Geraniaceae}, 
    \emph{Hydrangeaceae}, \emph{Malvaceae}, \emph{Oxalidaceae}, \emph{Primulaceae}, 
    \emph{Saxifragaceae}, \emph{Verbenaceae}.

    6+42=48
    \emph{Sapindaceae}

>>>>

    Only nine families were sufficiently well-represented to fit models for shared herbivores. Five of these were also well-represented in plant-pollinator networks: \emph{Asteraceae}, \emph{Fabaceae}, \emph{Melastomataceae}, \emph{Poaceae}, and \emph{Rubiaceae}. In total, there were 48 families which were well-represented enough to fit models for shared pollinators. Note that singular fits were obtained for \emph{Amaranthaceae}, \emph{Araliaceae}, \emph{Boraginaceae},
    \emph{Campanulaceae}, \emph{Caryophyllaceae}, \emph{Ericaceae}, \emph{Geraniaceae}, 
    \emph{Hydrangeaceae}, \emph{Malvaceae}, \emph{Oxalidaceae}, \emph{Primulaceae}, 
    \emph{Saxifragaceae}, and \emph{Verbenaceae}.
